---
title: "DATA 606 Project Proposal"
author: "Samuel I Kigamba"
date: "October 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data Preparation

```{r, message=FALSE, warning=FALSE}
# load data
#install.packages("fueleconomy")
library(plyr)
library(dplyr)
data("vehicles")
```

```{r}

write.csv(vehicles, file = "vehicles.csv")
vehicles <- read.csv(file = "vehicles.csv")

head(vehicles)

```
```{r, message=FALSE, warning=FALSE}
#vehicles <- read_csv("https://raw.githubusercontent.com/hadley/fueleconomy/master/data-raw/vehicles.csv", header = TRUE)
#head(vehicles)
```

### Research question
**You should phrase your research question in a way that matches up with the scope of inference your dataset allows for.**

Is the number of cylinders in a vehicle predictive of fuel economy?


### Cases 
**What are the cases, and how many are there?**

Each case represents a vehicle cylinders. There are (nrow <- length(vehicles$cyl)) 33,442 observations in the given data set.

```{r}
nrow <- length(vehicles$cyl)
nrow
```

### Data collection 
**Describe the method of data collection.**

Fuel economy data for all cars sold in the US from 1984 to 2015 is collected by the Environmental protection agency. (Source: https://www.fueleconomy.gov/feg/download.shtml). This is as a result of vehicle testing done at the Environmental Protection Agency's National Vehicle and Fuel Emissions Laboratory in Ann Arbor, Michigan, and by vehicle manufacturers with oversight by EPA.


### Type of study 
**What type of study is this (observational/experiment)?**

This is an observational study.

### Data Source
**If you collected the data, state self-collected. If not, provide a citation/link.**

Fuel economy data for all cars sold in the US from 1984 to 2015 is collected by the Environmental protection agency and is available online here (Source: https://www.fueleconomy.gov/feg/download.shtml). We have extracted it using fueleconomy package available under R (install.packages("fueleconomy")).

### Dependent Variable
**What is the response variable? Is it quantitative or qualitative?**

The response variable is the highway fuel consumption/economy and is numerical.

### Independent Variable
**You should have two independent variables, one quantitative and one qualitative.**

The independent variable is the number of cylinders (cyl) in the vehicles and is numerical.

### Relevant summary statistics
**Provide summary statistics for each the variables. Also include appropriate visualizations related to your research question (e.g. scatter plot, boxplots, etc). This step requires the use of R, hence a code chunk is provided below. Insert more code chunks as needed.**


```{r}
summary(vehicles$cyl)

hist(vehicles$cyl, breaks = 5)
```



```{r}
summary(vehicles$hwy)

hist(vehicles$hwy, breaks = 30)
line(vehicles$hwy)
```



```{r}
summary(vehicles$hwy)

plot(vehicles$cyl, vehicles$hwy)
```

```{r}
summary(vehicles$hwy)

plot(vehicles$hwy, vehicles$cyl)
```
